---
title: "PubMed Microbiome Analysis"
author: "Marguerite"
date: "2020-06-11"
output: html_document
---

I searched PubMed for Microbiome studies that included the term "microbiome" with "16s", "18s", or "ITS", "ITS1", or "ITS2" on June 11, 2020.


Plot of microbiome papers with any of these markers over time.
```{r}
require(xtable)
dat <- read.csv("PubMed_Timeline_Results_by_Year-all.csv", skip=1, header=T)
o <- order(dat$Year)
dat <- dat[o,]

with(data=dat, barplot(Count, Year))
with(data=dat, plot(Year, Count, type="b"))
total = sum(dat$Count)
datall <- dat
```
Total studies = `r total`

Now overlay other markers

```{r}
dat <- read.csv("PubMed_Timeline_Results_by_Year-18s.csv", skip=1, header=T)
o <- order(dat$Year)
dat <- dat[order(dat$Year),]
dat18s <- dat
names(dat18s)[2] <- "Count.L18s"

dat <- read.csv("PubMed_Timeline_Results_by_Year-ITS.csv", skip=1, header=T)
o <- order(dat$Year)
dat <- dat[order(dat$Year),]
datITS <- dat
names(datITS)[2] <- "Count.LITS"

dat <- merge(merge(datall, dat18s, all=T), datITS, all=T)
dat[is.na(dat)] <- 0
names(dat) <- c("Year", "All", "L18s", "LITS")
dat$L18sITS <- dat$L18s + dat$LITS

```

```{r}
with(data=dat, plot(Year, All, type="b", pch=19, col="red"))
with(data=dat, points(Year, L18s, type="b", pch=19, col="blue"))
with(data=dat, points(Year, L18sITS, type="b", pch=19, col="black"))
```

Use polygon to shade under plots and transparency
We need a function `makeTransparent()` to make transparent colors

```{r}
makeTransparent<-function(someColor, alpha=1)
{
  newColor<-col2rgb(someColor)
  apply(newColor, 2, function(curcoldata){rgb(red=curcoldata[1], blue=curcoldata[2],
    green=curcoldata[3],alpha=alpha*255, maxColorValue=255)})
}

with(data=dat, plot(Year, All, type="n"))
with(data=dat, polygon(x=c(Year, rev(Year)), y=c(All, rev(L18sITS)), col=makeTransparent("red",.3), border=NA))
with(data=dat, polygon(x=c(Year, rev(Year)), y=c(L18s, rev(L18sITS)), col=makeTransparent("black",.3), border=NA))
with(data=dat, polygon(x=c(Year, Year[1]), y=c(L18s, 0), col=makeTransparent("blue",.3), border=NA))

with(data=dat, lines(Year, All,  lwd=5, pch=19,  col="red"))
with(data=dat, lines(Year, L18s,  lwd=5, pch=19, col="blue"))
with(data=dat, lines(Year, L18sITS,  lwd=5, pch=19, col="black"))
```

If we cut it off at 2019 (incomplete reporting for 2020, so itʻs kind of misleading)  

```{r}
dat <- dat[dat$Year < 2020,]
with(data=dat, plot(Year, All, type="n"))
with(data=dat, polygon(x=c(Year, rev(Year)), y=c(All, rev(L18sITS)), col=makeTransparent("red",.3), border=NA))
with(data=dat, polygon(x=c(Year, rev(Year)), y=c(L18s, rev(L18sITS)), col=makeTransparent("black",.3), border=NA))
with(data=dat, polygon(x=c(Year, Year[1]), y=c(L18s, 0), col=makeTransparent("blue",.3), border=NA))

with(data=dat, lines(Year, L18s,  lwd=5, pch=19, col="blue"))
with(data=dat, lines(Year, L18sITS,  lwd=5, pch=19, col="black"))
with(data=dat, lines(Year, All,  lwd=5, pch=19,  col="red"))
legend(x=1995, y=3000, legend=c("All = 16s or 18s or ITS", "ITS = Fungi", "18s = Other Eukaryotes"), fill=c("red", "black", "blue"), text.col=c("red", "black", "blue"), text.font=2, bty="n")
```

Here is the data table
```{r kable}
require(knitr)
kable(dat, digits=1, col.names=c("Year", "All", "18s", "ITS", "18s+ITS"))
```
